Eval expressions

### 2021-01-05 analysis/expressions.Rmd
Most widespread expressions in terms of call sites/packages

E_raw -> E

C_raw -> C
corpus_size <- nrow(C)

```

>>>>

read_fst(calls_path) %>% as_tibble() -> E_raw

 E_raw %>% select(
    run_package = package, #      The package which was run to trigger the eval
    ev_variant = eval_function, # Which eval variant was called
    duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
    src_ref = eval_call_srcref, # Source ref for the eval call site
    file, #                       Script file name (name of this run)
    ev_package = eval_source, #   Package of the call site
    type = expr_resolved_type_tag,   #   Argument type
    ev_expr = expr_expression,
    expr_resolved,
    parsed = expr_parsed_expression
  ) -> E

C_raw -> C
corpus_size <- nrow(C)
```

Some useful numbers:
```{r}
nb_call_sites <- E %>% pull(src_ref) %>% n_distinct()
```

# Most frequent expressions

Before resolving, so as the programmer wrote them:

```{r}
E %>% count(ev_expr, wt = duplicates, sort = TRUE) 
```

After resolving:

```{r}
E %>% count(expr_resolved, wt = duplicates, sort = TRUE) 
```

# Expressions common to several call sites and packages

It emphasizes which expressions are a common pattern across various code bases.

```{r}
widespread_expr <- E %>% group_by(ev_expr) %>% summarize(n_call_sites = n_distinct(src_ref), n_packages = n_distinct(ev_package))
```

```{r}
widespread_expr %>% arrange(desc(n_call_sites)) %>% datatable()
```

```{r}
widespread_expr %>% arrange(desc(n_packages)) %>% datatable()
```

For instance, for the most widespread expression, both in terms of call sites and packages, `mf`, we show here the packages sorted by decreasing number of call sites with this expression name.

```{r}
E %>% filter(ev_expr == "mf") %>% group_by(ev_package) %>% summarise(n = n_distinct(src_ref)) %>% arrange(desc(n))
```

Manual inspection seems to show that `mf` is often used as a result of a `match.call`:

- https://github.com/cran/PMCMRplus/blob/4f5234542aa0a60642b230bea7efb668fb16a140/R/mandelkTest.R#L121 
- https://github.com/fbertran/plsRglm/blob/dfa4e54ea02bca8bf04d29bb65dc7dba611927c9/R/plsRglmmodel.default.R#L4

This is the common pattern when a call is retrieved and then modified, then evaluated.

# Expressions using `parse`, `str2lang`, and `str2expression`

```{r}
parsed_expr <- E %>% filter(!is.na(parsed))

nb_parsed_call_sites <- parsed_expr %>% pull(src_ref) %>% n_distinct()
```

There are `r nb_parsed_call_sites` call sites using those functions in their argument, out of the `r nb_call_sites` in total, i.e. `r ratio(nb_parsed_call_sites, nb_call_sites)`%.
